\documentclass{article}
\usepackage{fontspec}
\usepackage{xcolor}
%\usepackage{sagetex}

\usepackage{euler}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{unicode-math}


\usepackage[makeroom]{cancel}
\usepackage{ulem}

\setlength\parindent{0em}
\setlength\parskip{0.618em}
\usepackage[a4paper,lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}

\setmainfont[Mapping=tex-text]{Helvetica Neue LT Std 45 Light}

\newcommand\N{\mathbb{N}}
\newcommand\Z{\mathbb{Z}}
\newcommand\Q{\mathbb{Q}}
\newcommand\R{\mathbb{R}}
\newcommand\C{\mathbb{C}}
\newcommand\A{\mathbb{A}}

\usepackage{soul}
\begin{document}

\begin{center}
  151B --- 7

  RJ Acuna

  (862079740)
\end{center}\vspace{1.618em}

\paragraph{1} If the sequences $\{f_n\}$ and $\{g_n\}$ converge
uniformly on $E$, prove that $\{f_n+g_n\}$ converges uniformly on $E$.

\uwave{pf. }

Let $\{f_n\}$ and $\{g_n\}$ converge uniformly on $E\subseteq \R$.

So $\{f_n\}$ and $\{g_n\}$ are Cauchy sequences of functions
$\forall \varepsilon > 0:$

$f_n \rightarrow f \implies \exists M \in \N, \forall m_1 \geq M,
m_2\geq M, |f_{m_1} - f_{m_2}|<\frac{\varepsilon}{2}$

$g_n \rightarrow g \implies \exists K \in \N, \forall k_{1} \geq K,k_2
\geq K,$ $|g_{k_1}-g_{k_2}|<\frac{\varepsilon}{2}$

Let $N = \max \{M,K\}$, $\forall n\geq N,l\geq N$ we have both,

$|f_n - f_l|< \frac{\varepsilon}{2}$ and $|g_n - g_l|<\frac{\varepsilon}{2}$

$|f_n + g_n - f_l - g_l|\leq |f_n - f_l| + |g_n - g_l| \leq \varepsilon$

So, $\{f_n + g_n\}$ converges uniformly on $E$ $\quad \blacksquare$

\paragraph{2} If the sequences ${f_n}$ and ${g_n}$ defined on $E$ such that

$\quad$(1) $\sum f_n$ converges uniformly on $E$

$\quad$(2) $g_n$ converges to $0$ uniformly on $E$.

$\quad$(3) $g_1(x) ≥ g_2(x) ≥ g_3(x) ≥ \cdots$ for every $x ∈  E$

Prove that $\sum f_ng_n$ converge uniformly on E.

\uwave{pf.}

Let $S_n = \sum_{n=1}^{N} f_n$

$\sum f_n$ converges uniformly on $E\implies \{S_n\}$ is bounded.

So, $\exists M\in \R: |S_n|\leq M$ for all $n$.

$g_n\rightarrow 0$ uniformly  on $E$.

Let $\varepsilon > 0,$ there is an $N$ such that $g_N(x) \leq \frac{\varepsilon}{2M}$

From the third condition $g_n -g_{n+1}\geq 0$.

For $N \leq p \leq q$, we have
\begin{align*}
  \left| \sum_{n=1}^q f_n g_n - \sum_{n=1}^{p-1} f_ng_n \right|
  &= \left|\sum_{n=p}^q f_n g_n \right|\\
                  &= \left|\sum_{n=p}^{q-1}S_n(g_n - g_{n+1}) + S_qg_q -
                       S_{q-1}g_p\right| \\
  &\leq M \left|\sum_{n=p}^{q-1}(g_n - g_{n+1}) + g_q +
    g_p\right|\\
  &= 2Mg_p \leq 2Mg_{N}\leq \varepsilon
\end{align*}

So, $\{\sum_{n=1}^kf_ng_n\}$ converges uniformly by the Cauchy criterion.
Thus, $\sum_{n=1}^\infty f_ng_n \quad \blacksquare$

\paragraph{3} If $\sum |c_n| \leq \infty$ and $x_n$ is a sequence of
distinct points in $(a,b),$ show that
$$f(x) = \sum_{k=1}^\infty c_kI(x-x_k)$$

converges uniformly and that $f$ is continuous for every $x \neq x_n$.

\uwave{pf. }

Let $f(x) = \sum_{k=1}^\infty c_kI(x-x_k)$

$|c_nI(x-x_n)| \leq |c_n|$, and $\sum |c_n| \leq \infty$

By, theorem $7.10$, it follows that $f$ converges.

Let $S_n = \sum_{k=1}^n c_n I(x-x_n),$ and $\{S_n\}$ be the sequence
of partial sums of $f$.

Each $S_n$ is a linear combination of functions with discontinuities at
$\{x_k\}_{k=1}^n$, so $S_n$ is discontinuous precisely there.

So, all of the discontinuities of $\{S_n\}$ is the sequence $\{x_n\}$
of distinct points.

let $E = (a,b)\backslash \{x_n\}$, now since the discontinuities of
$\{S_n\}$ are not on $E$, $\forall n\in \N, S_n$ is continuous on $E$.

So, $\{S_n\}$ is a sequence of continous functions on $E$, that
converges uniformly to $f$ in $E$.

So, by theorem $7.12$ $f$ is
continuous on $E$.

Which is precisely the set of points $x \in (a,b),$
where $x \neq x_n$ for all $n\in \N \quad \blacksquare$

\paragraph{4} Suppose ${f_n}$ is an equicontinuous sequence of
functions on $[a, b]$ and $\{f_n\}$ converge pointwise on $[a,
b]$. Prove that it converges uniformly.

\uwave{pf. }


$\{f_n\}$ converges pointwise $\implies \forall x\in [a,b],
\{f_n(x)\}$ converges.

So by the Cauchy criterion for sequences of real numbers,

$\exists N\in \N: n\geq N, m\geq N \implies |f_n(x)-f_m(x)|\leq \frac{\varepsilon}{3}$

$\{f_n\}$ is equicontinuous $\implies \forall \varepsilon > 0, \exists
\delta >0: |x-y|<\delta \implies
|f_n(x)-f_n(y)|<\frac{\varepsilon}{3}$
\begin{align*}
  |f_n(x)-f_m(x)| &= |f_n(x)-f_m(x) +f_n(y)-f_n(y) +f_m(y)-f_m(y)| \\
                  &= |f_n(x)-f_n(y) +f_n(y)-f_m(y) -f_m(x) +f_m(y)| \\
                  &\leq |f_n(x)-f_n(y)|+|f_n(y)-f_m(y)|+|f_m(x)
                    -f_m(y)|\\
                  &\leq |f_n(x)-f_n(y)|+|f_n(y)-f_m(y)|+|f_m(x)
                    -f_m(y)|\\
                  &\leq \frac{2\varepsilon}{3} + |f_n(y)-f_m(y)|
                    \quad \text{ by equicontinuity of $\{f_n\}$}\\
                  &\leq \varepsilon
                    \hspace{3.4cm} \text{ by pointwise convergence of $\{f_n\}$}
\end{align*}

Since, $[a,b]$ so there exists a finite subcover by open balls of
radius $\delta/2$. Then $x$ lies in one of the
balls of radius $\delta/2$, so the previous inequality shows the Cauchy condition for uniform
convergence of functions holds for all $x\in [a,b]$.

Therefore, $\{f_n\}$ converges uniformly$\quad \blacksquare$

\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
